\fontfamily{phv}\selectfont{Research A Proposal}

### 2013-09-24 docs/proposal/doc.tex
merge

% vergelijking met granger causality, en andere methodes?

@@

@@

% Effective connectivity
% ...

\subsection*{Bayesian connectomics}
% ...

@@

>>>>

% vergelijking met granger causality, en andere methodes?
% granger (Alard Roebroeck, Elia Formisano, Rainer Goebel, 2005) -> geen structural connectivity nodig (schaalt niet goed)
% covariance structural equation modeling -> structural connectivity nodig (Roebroeck, Formisano, Goebel, 2005)
% Multivariate autoregressive modeling (Harrison, Penny, Friston) -> Set of interaccting regions chosen beforehand (Roebroeck, Formisano, Goebel, 2005)
% Dynamic causal modelling (Friston, Harrison, Penny, 2003) -> Set of interaccting regions chosen beforehand (Roebroeck, Formisano, Goebel, 2005)

@@

Much progress has recently been made in the fields of structural and functional connectivity\cite{vandenheuvel2010}.
Research has also been done on inferring effective connectivity, based on Granger causality (Roebroeck, Formisano, Goebel, 2005), multivariate autoregressive modeling (Harrison, Penny, Friston, 2003) and dynamic causal modelling (Friston, Harrison, Penny, 2003).
However, many challenges are still being faced. (Ramsey, Hanson, Hanson, Halchenko, Poldrack , Glymour)

@@

% Effective connectivity
%In contrast to functional and structural connectivity, effective connectivity takes into account the cause and effect of relations.
%It has been described as "the influence one neural system exerts over another" \cite{friston1994".
%Effective connectivity indicates which brain regions stimulate other regions.
%Time series need to be analysed to infer effective connectivity as cause and effect can be deduced from which event precedes which. 
%It is possible to infer effective connectivity from structural and functional connectivity.

@@

The causal discovery method which we will use is the PC-algorithm (spirtes, 2000). An advantage of this algorithm is that the scaling is relatively well.
